Lott and Mustard Replication Assignment

### 2022-04-14 tables/rep_table_1.tex
updates

\caption{\label{tab:tab:replicatetable2}Replication of Table 1}
\centering
\begin{tabular}[t]{lrr}
\toprule
Variable & Standard Deviation of State Means & Mean of Within-State Standard Deviations\\
\midrule
\cellcolor{gray!6}{Violent Crime Rate} & \cellcolor{gray!6}{306.62} & \cellcolor{gray!6}{78.19}\\
Property Crime Rate & 1135.99 & 422.15\\
\cellcolor{gray!6}{Murder Crime Rate} & \cellcolor{gray!6}{6.19} & \cellcolor{gray!6}{1.50}\\
Rape Crime Rate & 13.26 & 6.37\\
\cellcolor{gray!6}{Robbery Crime Rate} & \cellcolor{gray!6}{171.87} & \cellcolor{gray!6}{28.81}\\
\addlinespace
Assault Crime Rate & 144.28 & 57.62\\
\cellcolor{gray!6}{Burglary Crime Rate} & \cellcolor{gray!6}{372.52} & \cellcolor{gray!6}{181.39}\\
Larceny Crime Rate & 705.73 & 260.55\\
\cellcolor{gray!6}{Autotheft Crime Rate} & \cellcolor{gray!6}{210.57} & \cellcolor{gray!6}{82.24}\\
Violent Arrest Rate & 10.38 & 10.54\\
\addlinespace
\cellcolor{gray!6}{Property Arrest Rate} & \cellcolor{gray!6}{3.07} & \cellcolor{gray!6}{3.23}\\
Murder Arrest Rate & 17.26 & 29.23\\
\cellcolor{gray!6}{Rape Arrest Rate} & \cellcolor{gray!6}{11.15} & \cellcolor{gray!6}{10.65}\\
Assault Arrest Rate & 11.42 & 10.81\\
\cellcolor{gray!6}{Robery Arrest Rate} & \cellcolor{gray!6}{8.83} & \cellcolor{gray!6}{8.09}\\
\addlinespace
Burglary Arrest Rate & 3.08 & 3.20\\
\cellcolor{gray!6}{Larceny Arrest Rate} & \cellcolor{gray!6}{3.42} & \cellcolor{gray!6}{3.49}\\
Autotheft Arrest Rate & 10.67 & 31.62\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:replicatetable1}Replication of Table 1}
\centering
\begin{tabular}[t]{lrr}
\toprule
Variable & Standard Deviation of State Means & Mean of Within-State Standard Deviations\\
\midrule
\cellcolor{gray!6}{Violent Crime Rate} & \cellcolor{gray!6}{306.62} & \cellcolor{gray!6}{78.19}\\
Property Crime Rate & 1135.99 & 422.15\\
\cellcolor{gray!6}{Murder Crime Rate} & \cellcolor{gray!6}{6.19} & \cellcolor{gray!6}{1.50}\\
Rape Crime Rate & 13.26 & 6.37\\
\cellcolor{gray!6}{Assault Crime Rate} & \cellcolor{gray!6}{144.28} & \cellcolor{gray!6}{57.62}\\
\addlinespace
Robbery Crime Rate & 171.87 & 28.81\\
\cellcolor{gray!6}{Burglary Crime Rate} & \cellcolor{gray!6}{372.52} & \cellcolor{gray!6}{181.39}\\
Larceny Crime Rate & 705.73 & 260.55\\
\cellcolor{gray!6}{Autotheft Crime Rate} & \cellcolor{gray!6}{210.57} & \cellcolor{gray!6}{82.24}\\
Violent Arrest Rate & 10.38 & 10.54\\
\addlinespace
\cellcolor{gray!6}{Property Arrest Rate} & \cellcolor{gray!6}{3.07} & \cellcolor{gray!6}{3.23}\\
Murder Arrest Rate & 17.26 & 29.23\\
\cellcolor{gray!6}{Rape Arrest Rate} & \cellcolor{gray!6}{11.15} & \cellcolor{gray!6}{10.65}\\
Assault Arrest Rate & 11.42 & 10.81\\
\cellcolor{gray!6}{Robery Arrest Rate} & \cellcolor{gray!6}{8.83} & \cellcolor{gray!6}{8.09}\\
\addlinespace
Burglary Arrest Rate & 3.08 & 3.20\\
\cellcolor{gray!6}{Larceny Arrest Rate} & \cellcolor{gray!6}{3.42} & \cellcolor{gray!6}{3.49}\\
Autotheft Arrest Rate & 10.67 & 31.62\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-14 writing/paper.tex
edits to table 3 output
bacon decomp
updates

\usepackage{a4wide}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{parskip}
\doublespacing
\geometry{margin=1.5in}

@@

\textbf{Prompt: } Here you should describe the model that you will be using.  There are two models.

@@

	\textbf{Prompt: } This model should be similar to the one used by the authors only you will be using the state level data with state and year fixed effects plus all controls.  Choose the outcome specification (log or levels in rate form) that the authors use.

	\input{../tables/rep_table_3.tex}

@@

	\textbf{Prompt: } Implement the Bacon decomposition discussed in class, but unlike the previous section, only report the TWFE without controls (as we did not discuss the interpretation of the Bacon decomposition with controls in class).  It is also discussed in my Mixtape chapter in the Mixtape.  Interpret this.  Product Table 3 with this information.  The types of things I want you to focus on are the weights and average DiD estimate on the early to late 2x2s as well as the late to early 2x2s. Why are the late to early 2x2s a problem?  Read closely my section on this in the Mixtape to help you understand this problem.

>>>>

\usepackage{a4wide}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage{parskip}
\doublespacing
\geometry{margin=1.5in}

@@

\begin{itemize}
\item 
Explain what this section is going to be about at a high level
\item
Quickly Summarize anything interesting

\end{itemize}

@@

\begin{itemize}
\item 
Describe the model used by the authors
\item
Describe how this model is different
\item
Explain exclusion of controls from the tables but that they are analyzed
\item 
Draft explanation of model results
\end{itemize}

\input{../tables/rep_table_3a.tex}

\input{../tables/rep_table_3b.tex}

\input{../tables/rep_table_3c.tex}

@@

\begin{itemize}
\item
Explain Analysis: Bacon Decomposition without controls
\item
Explain weights and DiD estimates
\item
Explain early to late 2x2s and late to early 2x2s. What is the problem with late to early?
\end{itemize}

\begin{landscape}
\input{../tables/bacon_decompositiona.tex}

\input{../tables/bacon_decompositionb.tex}

\input{../tables/bacon_decompositionc.tex}

\end{landscape}
